use_---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# namechecker

<!-- badges: start -->
![R](https://img.shields.io/badge/r-%23276DC3.svg?style=for-the-badge&logo=r&logoColor=white)
![GitHub](https://img.shields.io/badge/github-%23121011.svg?style=for-the-badge&logo=github&logoColor=white)
<!-- badges: end -->

The package is designed to seamlessly interface with the WoRMS (World Register of Marine Species) API, 
providing a straightforward method for verifying the acceptance of species names. 
While there are other packages available that offer functionalities centered around the WoRMS API,
we found that many of them come with complex documentation and offer a multitude of tools that extend 
beyond our basic requirement of name validation. Our package aims to simplify this process by focusing 
solely on the essential task of checking the acceptance status of species names, making it more user-friendly 
and easier to navigate.

## Installation

You can install the development version of namechecker from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CBMC-GCMP/namechecker")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(namechecker)
library(dplyr)

species_list <- sample_species_names[c(1:3)]

final_data <- get_valid_names(species_list)

glimpse(final_data)

```


